\documentclass[oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
%
\usepackage{lmodern}
\usepackage{microtype}
%
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath,amssymb,amsfonts}

\input{common}

\SetOrganization{Primordial Machine's}
\SetLibraryName{One Zero Functors Library}
\SetLibraryVersion{v1.4}
\SetLibraryRepository{https://github.com/primordialmachine/one-zero-functors}
\SetAuthor{Michael Heilmann}
\SetEmail{michaelheilmann@primordialmachine.com}

\begin{document}
\maketitle
\tableofcontents
\section{Synopsis}
C++ 17 library providing extendable abstractions of the constants zero and one.\newline

\noindent{}This library provides functors which return the constant zero and one for most built-in types.
Furthermore, a consumer of this library can add additional partial specializations of these functors for arbitrary types.\newline

\noindent{}The library is made available publicly on
\href{\GetLibraryRepository}{Github}
under the
\href{\GetLibraryRepository/blob/master/LICENSE}{MIT License}.

\section{Requirements}
None.

\section{Limitations and Restrictions}
The library officially only supports Visual Studio 2017 and Windows 10.

\section{Introductory example}
\textit{\color{orange}This library does not provide any examples yet.}
%Examples are located in the \href{\GetLibraryRepository/blob/master/examples}{examples} directory.

\section{Building under Visual Studio 2017}
\begin{enumerate}
\item Open the solution \texttt{solution.sln} in Microsoft Visual Studio 2017.
\item Batch build everything.
\item The folder \texttt{packages} contains the distribution of the library i.e. include files and the
      static libraries for
  \begin{enumerate}
    \item the platforms \texttt{Win32} and \texttt{x64} and
    \item configurations \texttt{Release} and \texttt{Debug}.
  \end{enumerate}
\item Copy the contents of the \verb+packages+ folder into a directory. Let
      \verb+[library home]+ be a placeholder denoting the path by which that folder
      can be referenced from your project.
\item Add
  \begin{enumerate}
    \item the include path
\begin{verbatim}
[library home]/primordialmachine/one-zero-functors/
$(PlatformTarget.toLower())/$(Configuration.toLower())/includes
\end{verbatim}
	and
    \item the library path
\begin{verbatim}
[library home]/primordialmachine/one-zero-functors/
$(PlatformTarget.toLower())/$(Configuration.toLower())/libraries
\end{verbatim}
    to your project.
\end{enumerate}
\item Link your project with the library \verb+one-zero-functors.lib+.
\item Add the include directive \verb+#include "primordialmachine/one_zero_functors/include.hpp"+ where appropriate.
\item You can now use the functionality provided by the library.
\end{enumerate}

\section{Library Interface Documentation}

\subsection{\texttt{namespace primordialmachine}}
The namespace this library is adding its declarations/definitions to.
The added namespace elements are documented below.

\subsection{\texttt{zero\_functor<TYPE>}}
\begin{verbatim}
template<typename TYPE>
struct zero_functor;
\end{verbatim}
Provides a const constexpr noexcept \texttt{operator()} which receives zero arguments and returns a
value of type \texttt{TYPE} approximating the value $0$ (zero).
Specializations for the types
\texttt{char},
\texttt{signed char},
\texttt{unsigned char},
\texttt{signed short int}       (aka \texttt{short int},     aka \texttt{signed short},     aka \texttt{short}),
\texttt{signed long int}        (aka \texttt{long int},      aka \texttt{signed long},      aka \texttt{long}),
\texttt{signed long long int}   (aka \texttt{long long int}, aka \texttt{signed long long}, aka \texttt{long long}),
\texttt{unsigned short int}     (aka \texttt{unsigned short}),
\texttt{unsigned long int}      (aka \texttt{unsigned long}), and
\texttt{unsigned long long int} (aka \texttt{unsigned long long}),
\texttt{float},
\texttt{double}, and
\texttt{long double}
are provided.

\subsection{\texttt{one\_functor<TYPE>}}
\begin{verbatim}
template<typename TYPE>
struct one_functor;
\end{verbatim}
Provides a const constexpr noexcept \texttt{operator()} which receives zero arguments and returns a
value of type \texttt{TYPE} approximating the value $1$ (one).
Specializations for the types
\texttt{char},
\texttt{signed char},
\texttt{unsigned char},
\texttt{signed short int}       (aka \texttt{short int},     aka \texttt{signed short},     aka \texttt{short}),
\texttt{signed long int}        (aka \texttt{long int},      aka \texttt{signed long},      aka \texttt{long}),
\texttt{signed long long int}   (aka \texttt{long long int}, aka \texttt{signed long long}, aka \texttt{long long}),
\texttt{unsigned short int}     (aka \texttt{unsigned short}),
\texttt{unsigned long int}      (aka \texttt{unsigned long}), and
\texttt{unsigned long long int} (aka \texttt{unsigned long long}),
\texttt{float},
\texttt{double}, and
\texttt{long double}
are provided.

\subsection{\texttt{zero<TYPE>()}}
Function returning an approximation of type \texttt{TYPE} of the value $0$ (zero).
\begin{verbatim}
template<typename TYPE>
constexpr auto zero() -> decltype(zero_functor<TYPE>()())
{ return zero_functor<TYPE>()(); }
\end{verbatim}

\noindent{}Provides a constexpr \texttt{operator()} which receives zero arguments and returns a value of type
\texttt{decltype\allowbreak(zero\allowbreak\_functor\allowbreak<TYPE>\allowbreak()())} approximating the value $0$ (zero).
The function is noexcept if \texttt{zero\allowbreak\_\allowbreak functor<TYPE>()()} is noexcept otherwise not.

\subsection{\texttt{one<TYPE>()}}
Function returning an approximation of type \texttt{TYPE} of the value $1$ (one).
\begin{verbatim}
template<typename TYPE>
constexpr auto one() -> decltype(one_functor<TYPE>()())
{ return one_functor<TYPE>()(); }
\end{verbatim}

\noindent{}Provides a constexpr \texttt{operator()} which receives zero arguments and returns a value of type
\texttt{decltype(one\allowbreak\_functor\allowbreak<TYPE>\allowbreak()())} approximating the value $1$ (one).
The function is noexcept if \texttt{one\allowbreak\_\allowbreak functor<TYPE>()()} is noexcept otherwise not.

\end{document}
